---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 7th August, refers to a single outcome analysis (Daytime impairment) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->
```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
library(xlsx)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoIncludedAllOutcomesClean27.6dVirgiRenamedInterventions.xlsx", na = "NA")


```

```{r, include=FALSE}
# prepare the data
DATApairs=pairwise(treat=Drug_name, mean=DayTimeSleepinessScaleMean, sd=DayTimeSleepinessScaleSD, n=DayTimeSleepinessScaleParticipants, data=DATA, studlab = Study_name, sm= "SMD")

# check there is no NA is the data
DPs <- DATApairs[!is.na(DATApairs$TE) & !is.na(DATApairs$seTE),]

# remove studies with "special patients" that should not be included in main analysis
#DPs <- DPs[DPs$Included==1,]

#check p-value availability for paired t-test for crossover studies with both phases used
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,c("studlab","Day_PorF-value","Day_p=0, f=1")]
# remove studies wit no p-value
DPs <- DPs[DPs$studlab!="Vinkari 1984" & DPs$studlab!="Pigeon 2010",]
# only parallel study for this outcome so no adjustment and no need for sensitivity

# save adjusted pairwise dataset for MAs
write.csv(DPs, file = "~/Virginia/NMA insomnia/DaytimeImpairment_pairwise.csv")


# run netconnection first to check for potential sub-networks
netconnection(treat1,treat2,studlab,data=DPs,warn = T)

#remove rows for studies disconnected from main network
DPs <- subset(DPs,treat2!="waitlist")



DPs1 <- DPs[-grep("chlormethiazole|triazolam|loprazolam|nitrazepam|zopiclone",DPs$treat2),]
DI1<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs1, sm="SMD",r="pbo",comb.fixed =F, comb.random = T)
DI1


```

## Description of the network


This network formed by studies examining the outcome Daytime impairment is composed by two sub-networks.
The following treatments were excluded as they were disconnected to the two main sub-networks:

* Mindfulness Based Stress Reduction Program
* waitlist
* sleep hygiene
* lormetazepam + sleep hygiene
* artificial juice
* tart cherry juice 

The only crossover study for this outcome (Vinkari 1984) was excluded as it had no available p-value needed to calculate the adjusted standard error.

### Sub-network 1

Below is a description for the sub-network including the following interventions

```{r, echo=FALSE}
DI1$trts
```


Number of included interventions:
```{r, echo=FALSE}
DI1$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
DI1$k
```
\    

  
 The plot below shows the available data\
```{r, echo=FALSE}
#network plot
netgraph(DI1, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```




## Frequentist network meta-analysis 

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(DI1, ref="pbo", sortvar = -Pscore,xlab="MD")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leagueDI1 <- netleague(DI1, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leagueDI1$random, file = "leagueDI1-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(DI1$tau,3)))
```
and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(DI1$I2, digits = 2)*100,"%"))
```

<!-- There is little/no/important evidence of inconsistency in the data. There are in total -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- split=netsplit(SOL) -->
<!-- SIDEp=split$compare.random$p -->
<!-- SIDEp=SIDEp[!is.na(SIDEp)] -->
<!-- #proportion of inconsistent loops -->
<!-- cat(length(SIDEp)) -->
<!-- ``` -->

<!-- comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in -->

<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(length(SIDEp[SIDEp<=0.1])) -->
<!-- ``` -->
<!-- loops which gives a % of inconsistent loops equal to -->
<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%")) -->
<!-- ``` -->



<!-- The p-value from the design-by-treatment test is -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- a=decomp.design(SOL) -->
<!-- print(round(a$Q.inc.random$pval,3)) -->
<!-- ``` -->


```{r, include=FALSE}
DI2 <- netmeta(TE,seTE,treat1,treat2,studlab,data=DPs, subset = grep("chlormethiazole|loprazolam|nitrazepam",DPs$treat1), sm="SMD",r="chlormethiazole",comb.fixed =T, comb.random = F)
DI2
```

### Sub-network 2

Below is a description for the sub-network including the following interventions

```{r, echo=FALSE}
DI2$trts
```


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included interventions:
```{r, echo=FALSE}
DI2$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
DI2$k
```



The plot below shows the available data

```{r, echo=FALSE}

#network plot
netgraph(DI2, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1)
```

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(DI2, ref="chlormethiazole", sortvar = -Pscore,xlab="SMD")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leagueDI2 <- netleague(DI2, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leagueDI2$random, file = "leagueDI2-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```
<!-- The P-scores (equivalent to the SUCRAs) are shown below -->
<!-- ```{r, echo=FALSE} -->
<!-- netrank(SQ2) -->
<!-- ``` -->

<!-- The heterogeneity standard deviation is estimated at -->
<!-- ```{r, echo=FALSE} -->
<!-- cat(paste("tau=",round(SQ2$tau,3))) -->
<!-- ``` -->
<!-- and I-square (total) is  -->
<!-- ```{r, echo=FALSE} -->
<!-- cat(paste("I2=",round(SQ1$I2),"%")) -->
<!-- ``` -->

