---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 7th August, refers to a single outcome analysis (Paradoxical drug reactions/Anxiety) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->


```{r, include=FALSE}
library(devtools)
# install_github("esm-ispm-unibe-ch/NMAJags")
# library(NMAJags)
# library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
library(xlsx)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoClean27.6eVirgiRenamedIntervSideEffectsClean.xlsx", na = "NA")


```



```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=Drug_name, event=`Anxiety/Agitation`, n=`N_arm_total_for sideeffects`, data=DATA, studlab = Study_name, sm= "OR")
#run NMA and create an object called EFF for efficacy   ### gives error because consists of 5 separate sub-networks so run netconnection first
netconnection(treat1,treat2,studlab,data=DATApairs,warn = T)
#remove rows for studies disconnected from main network
DPs <- DATApairs[-grep("LAT|MAT|BBT I|Mindfulness|massage|hygiene|juice|acupressure|acupuncture",DATApairs$treat1),]

# remove interventions disconnected to main network (also have NA TE and seTE)
DPs <- DPs[-grep("therapeutic|midazolam",DPs$treat2),]

# remove studies with "special patients" that should not be included in main analysis
DPs <- DPs[DPs$Included==1,]

# remove studies with missing TE or seTE 
DPs <- DPs[!is.na(DPs$TE),]

netconnection(treat1,treat2,studlab,data=DPs,warn = T)

# 2 sub-networks
DPs1 <- DPs[DPs$treat2!="triazolam",]


pdrAE1<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs1,  sm="OR",r="pbo",comb.fixed =F, comb.random = T)
pdrAE1

```
## Description of the network


This network formed by studies examining the outcome Paradoxical Drug Reactions is composed by two sub-networks.

<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
### Sub-network 1

Below is a description for the sub-network including the following interventions
```{r, echo=FALSE}
pdrAE1$trts
```

Number of included interventions:
```{r, echo=FALSE}
pdrAE1$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pdrAE1$k
```

The following treatments were excluded as they were disconnected to the main network:

* MAT
* LAT
* MAT+LAT
* massage
* therapeutic touch
* control/no intervention
* mimic therapeutic touch
* Mindfulness Based Stress Reduction Program
* waitlist
* sleep hygiene
* lormetazepam + sleep hygiene
* BBT I
* self-monitoring control
* auricular acupuncture
* control?
* acupressure
* sham acupressure
* artificial juice
* tart cherry juice 
* midazolam
* oxazepam
  
\    

  
 The plot below shows the available data\
```{r, echo=FALSE}
#network plot
netgraph(pdrAE1, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```




## Frequentist network meta-analysis 

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(pdrAE1, ref="pbo", sortvar = -Pscore,xlab="OR")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leaguePDR1 <- netleague(pdrAE1, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leaguePDR1$random, file = "leaguePDR1-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```


<!-- The P-scores (equivalent to the SUCRAs) are shown below -->
<!-- ```{r, echo=FALSE} -->
<!-- netrank(TST, small.values = "bad") -->
<!-- ``` -->

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(pdrAE1$tau,3)))
```
and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(pdrAE1$I2, digits = 2)*100,"%"))
```



<!-- There is little/no/important evidence of inconsistency in the data. There are in total -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- split=netsplit(TST) -->
<!-- SIDEp=split$compare.random$p -->
<!-- SIDEp=SIDEp[!is.na(SIDEp)] -->
<!-- #proportion of inconsistent loops -->
<!-- cat(length(SIDEp)) -->
<!-- ``` -->

<!-- comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in -->

<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(length(SIDEp[SIDEp<=0.1])) -->
<!-- ``` -->
<!-- loops which gives a % of inconsistent loops equal to -->
<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%")) -->
<!-- ``` -->



<!-- The p-value from the design-by-treatment test is -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- a=decomp.design(TST) -->
<!-- print(round(a$Q.inc.random$pval,3)) -->
<!-- ``` -->

```{r, include=FALSE}
pdrAE2 <- netmeta(TE,seTE,treat1,treat2,studlab,data=DPs, subset = DPs$treat2=="triazolam", sm="OR",r="chlormethiazole",comb.fixed =F, comb.random = T)
pdrAE2
```

### Sub-network 2

Below is a description for the sub-network including the following interventions


```{r, echo=FALSE}
pdrAE2$trts
```


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included interventions:
```{r, echo=FALSE}
pdrAE2$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
pdrAE2$k
```


The plot below shows the available data

```{r, echo=FALSE}

#network plot
netgraph(pdrAE2, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1)
```

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(pdrAE2, ref="chlormethiazole", sortvar = Pscore,xlab="OR")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leaguePDR2 <- netleague(pdrAE2, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leaguePDR2$random, file = "leaguePDR2-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```

<!-- The heterogeneity standard deviation is estimated at -->
<!-- ```{r, echo=FALSE} -->
<!-- cat(paste("tau=",round(SQ2$tau,3))) -->
<!-- ``` -->
<!-- and I-square (total) is  -->
<!-- ```{r, echo=FALSE} -->
<!-- cat(paste("I2=",round(SQ1$I2),"%")) -->
<!-- ``` -->