---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 4th October, refers to sensitivity analyses for a single outcome (Total Sleep Time) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->


```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
library(xlsx)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoClean30.9VirgiRenamedIntervSideEffectsClean.xlsx", na = "NA")


```



```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=Drug_name,mean=SleepTimeTotalScaleMean,sd=SleepTimeTotalScaleSD,n=SleepTimeTotalScaleParticipants, data=DATA, studlab = Final_ID_all, sm= "MD")
#run NMA and create an object called EFF for efficacy   ### gives error because consists of 5 separate sub-networks so run netconnection first
netconnection(treat1,treat2,studlab,data=DATApairs,warn = T)
#remove rows for studies disconnected from main network
DPs <- DATApairs[-grep("LAT|MAT|BBT I|midazolam|hygiene|juice",DATApairs$treat1),]
# save studies with "special patients" in separate dataframe
DPs_PsychogerPts <- DPs[DPs$Included==2,]

#check p-value availability for paired t-test for crossover studies with both phases used
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,c("studlab","tst_PorF-value","tst_p=0, f=1")]
# use threshold value for those with p-value <0.001
DPs[DPs$studlab==185, "tst_PorF-value"] <- 0.00099
#now calculate adjusted SE for remaining crossover studies
DPs$tvalue <- qt(as.numeric(DPs$`tst_PorF-value`)/2, df=DPs$n1-1, lower.tail = F)
#DPs$SDd <- abs((DPs$mean2-DPs$mean1)/DPs$tvalue*sqrt(DPs$n1))
#DPs$rho <- (DPs$sd1^2 + DPs$sd2^2 - DPs$SDd^2)/(2*DPs$sd1*DPs$sd2)
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,"seTE"] <- (abs(DPs$TE)/DPs$tvalue)[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1] 


#   EFF<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="SMD",r="pbo",comb.fixed =F, comb.random = T, tol.multiarm = 0.05, details.chkmultiarm = T)    
    ### gives error: Problems in multi-arm studies! Studies with negative treatment   arm variance: '18', '185'

# assign correlation value to study 18 and 185 based on other studies to fix issues with negative variances
DPs$rho <- 0.9
DPs$SDd <- sqrt(DPs$sd1^2 + DPs$sd2^2 - 2*DPs$rho*DPs$sd1*DPs$sd2)
DPs[DPs$studlab==18 | DPs$studlab==185,"seTE"] <- (DPs$SDd/sqrt(DPs$n1))[DPs$studlab==18 | DPs$studlab==185] 
TST_s1<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="MD",r="pbo",comb.fixed =F, comb.random = T, tol.multiarm = 0.5)
TST_s1

```
## Description of the network - sensitivity analysis 1 (include Psychogeriatric patients)


Below is a description for the network formed by studies examining the outcome Total Sleep Time also in Psychogeriatric patients.


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included interventions:
```{r, echo=FALSE}
TST_s1$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
TST_s1$k
```

The following treatments were excluded as they were disconnected to the main network:

  * MAT
  * LAT
  * MAT+LAT
  * sleep hygiene
  * lormetazepam + sleep hygiene
  * BBT I
  * self-monitoring control
  * midazolam
  * oxazepam
  * artificial juice
  * tart cherry juice  
  
\    

  
 The plot below shows the available data\
```{r, echo=FALSE}
#network plot
netgraph(TST_s1, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```




## Frequentist network meta-analysis 

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(TST_s1, ref="pbo", sortvar = -Pscore,xlab="MD")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leagueTST_s1 <- netleague(TST_s1, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leagueTST_s1$random, file = "leagueTST_s1-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```


<!-- The P-scores (equivalent to the SUCRAs) are shown below -->
<!-- ```{r, echo=FALSE} -->
<!-- netrank(TST, small.values = "bad") -->
<!-- ``` -->

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(TST_s1$tau,3)))
```
and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(TST_s1$I2, digits = 2)*100,"%"))
```





```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data for sensitivity analysis by drug group
DATA2 <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoClean4.10VirgiRenamedIntervSideEffectsClean.xlsx", na = "NA")


```

```{r, include=FALSE}
#prepare the data
DATApairs2=pairwise(treat=`Drug Group`,mean=SleepTimeTotalScaleMean,sd=SleepTimeTotalScaleSD,n=SleepTimeTotalScaleParticipants, data=DATA2, studlab = Final_ID_all, sm= "MD")
#run NMA and create an object called EFF for efficacy   ### gives error because consists of 5 separate sub-networks so run netconnection first
netconnection(treat1,treat2,studlab,data=DATApairs2,warn = T)
#remove rows for studies disconnected from main network
DPs2 <- DATApairs2[-grep("LAT|MAT|BBT I|hygiene|juice",DATApairs2$treat1),]
# # save studies with "special patients" in separate dataframe
# DPs_PsychogerPts <- DPs[DPs$Included==2,]
# 
#check p-value availability for paired t-test for crossover studies with both phases used
DPs2[DPs2$Crossoverstudy==1 & DPs2$`crossover, not first phase used`==1,c("studlab","tst_PorF-value","tst_p=0, f=1")]
# use threshold value for those with p-value <0.001
DPs2[DPs2$studlab==185, "tst_PorF-value"] <- 0.00099
#now calculate adjusted SE for remaining crossover studies
DPs2$tvalue <- qt(as.numeric(DPs2$`tst_PorF-value`)/2, df=DPs2$n1-1, lower.tail = F)
# #DPs$SDd <- abs((DPs$mean2-DPs$mean1)/DPs$tvalue*sqrt(DPs$n1))
# #DPs$rho <- (DPs$sd1^2 + DPs$sd2^2 - DPs$SDd^2)/(2*DPs$sd1*DPs$sd2)
DPs2[DPs2$Crossoverstudy==1 & DPs2$`crossover, not first phase used`==1,"seTE"] <- (abs(DPs2$TE)/DPs2$tvalue)[DPs2$Crossoverstudy==1 & DPs2$`crossover, not first phase used`==1] 

#   EFF<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="SMD",r="pbo",comb.fixed =F, comb.random = T, tol.multiarm = 0.05, details.chkmultiarm = T)
    ### gives error: Problems in multi-arm studies! Studies with negative treatment   arm variance: '18'

# assign correlation value to study 18 based on other studies to fix issues with negative variances
DPs2$rho <- 0.9
DPs2$SDd <- sqrt(DPs2$sd1^2 + DPs2$sd2^2 - 2*DPs2$rho*DPs2$sd1*DPs2$sd2)
DPs2[DPs2$studlab==18,"seTE"] <- (DPs2$SDd/sqrt(DPs2$n1))[DPs2$studlab==18]
TST_s2<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs2,  sm="MD",r="pbo",comb.fixed =F, comb.random = T, tol.multiarm = 0.5)
TST_s2

```
## Description of the network - sensitivity analysis 2 (by drug group)


Below is a description for the network formed by studies examining the outcome Total Sleep Time analysed by drug groups.


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included drug groups:
```{r, echo=FALSE}
TST_s2$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
TST_s2$k
```

The following treatments were excluded as they were disconnected to the main network:

  * MAT
  * LAT
  * MAT+LAT
  * sleep hygiene
  * lormetazepam + sleep hygiene
  * BBT I
  * self-monitoring control
  * artificial juice
  * tart cherry juice

Other studies have also been excluded prior to the sensitivity analysis if they were comparing two interventions of the same "drug group".

\


 The plot below shows the available data\
```{r, echo=FALSE}
#network plot
netgraph(TST_s2, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```




## Frequentist network meta-analysis

Below are the relative treatment effects from the NMA model.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(TST_s2, ref="pbo", sortvar = -Pscore,xlab="MD")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leagueTST_s2 <- netleague(TST_s2, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leagueTST_s2$random, file = "leagueTST_s2-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```


<!-- The P-scores (equivalent to the SUCRAs) are shown below -->
<!-- ```{r, echo=FALSE} -->
<!-- netrank(TST, small.values = "bad") -->
<!-- ``` -->

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(TST_s2$tau,3)))
```
and I-square (total) is
```{r, echo=FALSE}
cat(paste("I2=",round(TST_s2$I2, digits = 2)*100,"%"))
```
