---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 7th August, refers to a single outcome analysis (Patient subjective wellbeing/Quality of life) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->
```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoIncludedAllOutcomesClean27.6dVirgiRenamedInterventions.xlsx", na = "NA")


```

```{r, include=FALSE}
# prepare the data
DATApairs=pairwise(treat=Drug_name, mean=Qol_mean, sd=Qol_SD, n=QoL_participants, data=DATA, studlab = Study_name, sm= "SMD")

# run netconnection first to check for potential sub-networks
netconnection(treat1,treat2,studlab,data=DATApairs,warn = T)

#remove rows for studies disconnected from main network
DPs <- DATApairs[-grep("LAT|MAT|acupressure",DATApairs$treat1),]

# remove studies with "special patients" that should not be included in main analysis
# DPs <- DPs[DPs$Included==1,]


# check there is no NA is the data
DPs[is.na(DPs$TE) | is.na(DPs$seTE),c("studlab","treat1","treat2","TE","seTE")]
#DPs <- subset(DPs, studlab!="McCall 2006")


QOL<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs, sm="SMD",r="pbo",comb.fixed =F, comb.random = T)
QOL


```

## Description of the network


Below is a description for the network formed by studies examining the outcome Quality of Life.
The following treatments were excluded as they were disconnected to the two main networks:

  * MAT
  * LAT
  * MAT+LAT
  * acupressure
  * sham acupressure


Number of included interventions:
```{r, echo=FALSE}
QOL$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
QOL$k
```
\    

  
 The plot below shows the available data\
```{r, echo=FALSE}
#network plot
netgraph(QOL, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```




## Frequentist network meta-analysis 

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(QOL, ref="pbo", sortvar = -Pscore,xlab="MD")
```

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(QOL$tau,3)))
```
and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(QOL$I2, digits = 2)*100,"%"))
```

<!-- There is little/no/important evidence of inconsistency in the data. There are in total -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- split=netsplit(SOL) -->
<!-- SIDEp=split$compare.random$p -->
<!-- SIDEp=SIDEp[!is.na(SIDEp)] -->
<!-- #proportion of inconsistent loops -->
<!-- cat(length(SIDEp)) -->
<!-- ``` -->

<!-- comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in -->

<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(length(SIDEp[SIDEp<=0.1])) -->
<!-- ``` -->
<!-- loops which gives a % of inconsistent loops equal to -->
<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%")) -->
<!-- ``` -->



<!-- The p-value from the design-by-treatment test is -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- a=decomp.design(SOL) -->
<!-- print(round(a$Q.inc.random$pval,3)) -->
<!-- ``` -->

