---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 16th August, refers to a single outcome analysis (Heart attack) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->


```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
library(xlsx)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoClean27.6eVirgiRenamedIntervSideEffectsClean.xlsx", na = "NA")


```



```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=Drug_name, event=heart_attack_ischaemic_episode, n=`N_arm_total_for sideeffects`, data=DATA, studlab = Study_name, sm= "OR")
# remove studies with missing TE or seTE 
DPs <- DATApairs[!is.na(DATApairs$TE),]

# remove Dement 1991 because only data for one comparison so gives error when running netmeta
DPs <- DPs[DPs$studlab!="Overstall 1987",]

netconnection(treat1,treat2,studlab,data=DPs,warn = T)

#remove rows for studies disconnected from main network
DPs <- subset(DPs,treat1!="chlormethiazole")

# remove studies with "special patients" that should not be included in main analysis
#DPs <- DPs[DPs$Included==1,]



HA<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="OR",r="pbo",comb.fixed =F, comb.random = T)
HA

```
## Description of the network


Below is a description for the network formed by studies examining the outcome Heart Attack.


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included interventions:
```{r, echo=FALSE}
HA$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
HA$k
```

The following treatments were excluded as they were disconnected to the main network:

* chlormethiazole
* triazolam


The multiarm study Overstall 1987 was also excluded because data was not available for all comparisons.
\    

  
 The plot below shows the available data\
```{r, echo=FALSE}
#network plot
netgraph(HA, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```




## Frequentist network meta-analysis 

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(HA, ref="pbo", sortvar = -Pscore,xlab="OR")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leagueHA <- netleague(HA, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leagueHA$random, file = "leagueHeartAtt-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```

<!-- The P-scores (equivalent to the SUCRAs) are shown below -->
<!-- ```{r, echo=FALSE} -->
<!-- netrank(TST, small.values = "bad") -->
<!-- ``` -->

<!-- The heterogeneity standard deviation is estimated at -->
<!-- ```{r, echo=FALSE} -->
<!-- cat(paste("tau=",round(IDF$tau,3))) -->
<!-- ``` -->
<!-- and I-square (total) is  -->
<!-- ```{r, echo=FALSE} -->
<!-- cat(paste("I2=",round(IDF$I2, digits = 2)*100,"%")) -->
<!-- ``` -->



<!-- There is little/no/important evidence of inconsistency in the data. There are in total -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- split=netsplit(TST) -->
<!-- SIDEp=split$compare.random$p -->
<!-- SIDEp=SIDEp[!is.na(SIDEp)] -->
<!-- #proportion of inconsistent loops -->
<!-- cat(length(SIDEp)) -->
<!-- ``` -->

<!-- comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in -->

<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(length(SIDEp[SIDEp<=0.1])) -->
<!-- ``` -->
<!-- loops which gives a % of inconsistent loops equal to -->
<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%")) -->
<!-- ``` -->



<!-- The p-value from the design-by-treatment test is -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- a=decomp.design(TST) -->
<!-- print(round(a$Q.inc.random$pval,3)) -->
<!-- ``` -->

