---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 7th August, refers to a single outcome analysis (Number of nocturnal awakenings) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->


```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoIncludedAllOutcomesClean27.6dVirgiRenamedInterventions.xlsx", na = "NA")


```



```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=Drug_name,mean=NocturnalAwakeningsScaleMean,sd=NocturnalAwakeningsScaleSD,n=NocturnalAwakeningsScaleParticipants, data=DATA, studlab = Study_name, sm= "MD")

# check there is no NA is the data
DPs <- DATApairs[!is.na(DATApairs$TE) & !is.na(DATApairs$seTE),]


#check p-value availability for paired t-test for crossover studies with both phases used
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,c("studlab","Awak_PorF-value","Awak_p=0, f=1")]
# use threshold value for those with p-value <0.001
DPs[DPs$studlab=="Glass 2008", "Awak_PorF-value"] <- 0.00099
#now calculate adjusted SE for remaining crossover studies
DPs$tvalue <- qt(as.numeric(DPs$`Awak_PorF-value`)/2, df=DPs$n1-1, lower.tail = F)
#DPs$SDd <- abs((DPs$mean2-DPs$mean1)/DPs$tvalue*sqrt(DPs$n1))
#DPs$rho <- (DPs$sd1^2 + DPs$sd2^2 - DPs$SDd^2)/(2*DPs$sd1*DPs$sd2)
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,"seTE"] <- (abs(DPs$TE)/DPs$tvalue)[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1] 

# save adjusted pairwise dataset for MAs
write.csv(DPs, file = "~/Virginia/NMA insomnia/NumNocturnalAwakenings_pairwise.csv")


# assign correlation value to study 18 and 185 based on other studies to fix issues with negative variances
DPs$rho <- 0.9
DPs$SDd <- sqrt(DPs$sd1^2 + DPs$sd2^2 - 2*DPs$rho*DPs$sd1*DPs$sd2)
DPs[DPs$studlab=="Glass 2008","seTE"] <- (DPs$SDd/sqrt(DPs$n1))[DPs$studlab=="Glass 2008"] 


#run NMA and create an object called EFF for efficacy   ### gives error because consists of 5 separate sub-networks so run netconnection first
netconnection(treat1,treat2,studlab,data=DPs,warn = T)
#remove rows for studies disconnected from main network
DPs <- DPs[-grep("BBT I|hygiene",DPs$treat1),]
# remove studies with "special patients" that should not be included in main analysis
#DPs <- DPs[DPs$Included==1,]



NNA<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="MD",r="pbo",comb.fixed =F, comb.random = T)
NNA

```
## Description of the network


Below is a description for the network formed by studies examining the outcome Number of Nocturnal Awakenings.


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included interventions:
```{r, echo=FALSE}
NNA$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
NNA$k
```

The following treatments were excluded as they were disconnected to the main network:

  * sleep hygiene
  * lormetazepam + sleep hygiene
  * BBT I
  * self-monitoring control
  
\    

  
 The plot below shows the available data\
```{r, echo=FALSE}
#network plot
netgraph(NNA, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```




## Frequentist network meta-analysis 

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(NNA, ref="pbo", sortvar = -Pscore,xlab="MD")
```


<!-- The P-scores (equivalent to the SUCRAs) are shown below -->
<!-- ```{r, echo=FALSE} -->
<!-- netrank(TST, small.values = "bad") -->
<!-- ``` -->

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(NNA$tau,3)))
```
and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(NNA$I2, digits = 2)*100,"%"))
```



<!-- There is little/no/important evidence of inconsistency in the data. There are in total -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- split=netsplit(TST) -->
<!-- SIDEp=split$compare.random$p -->
<!-- SIDEp=SIDEp[!is.na(SIDEp)] -->
<!-- #proportion of inconsistent loops -->
<!-- cat(length(SIDEp)) -->
<!-- ``` -->

<!-- comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in -->

<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(length(SIDEp[SIDEp<=0.1])) -->
<!-- ``` -->
<!-- loops which gives a % of inconsistent loops equal to -->
<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%")) -->
<!-- ``` -->



<!-- The p-value from the design-by-treatment test is -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- a=decomp.design(TST) -->
<!-- print(round(a$Q.inc.random$pval,3)) -->
<!-- ``` -->


### Sensitivity analyses and meta-regressions

We run a sensitivity analyses excluding the crossover studies
```{r, include=FALSE}

#only non-crossover
InsoNNAsen=subset(DPs,Crossoverstudy==0 | Crossoverstudy==1 & `crossover, not first phase used`!=1)  
netconnection(treat1,treat2,studlab,data=InsoNNAsen,warn = T)

NNAsens<-netmeta(TE,seTE,treat1,treat2,studlab,data=InsoNNAsen,  sm="MD",comb.fixed =F, comb.random = T)
NNAsens


```

```{r, echo=FALSE}
#network plot
netgraph(NNAsens, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```

One study, comparing chlormethiazole versus temazepam, was also excluded from this sensitivity analysis because disconnected to the rest of the network

```{r, echo=FALSE}

forest(NNAsens, ref="pbo",sortvar = -Pscore, smlab="Only parallel studies", fontsize=10,xlab="MD")


```
