---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 7th August, refers to a single outcome analysis (Total sleep time by polysomnography) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->
```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
library(xlsx)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoIncludedAllOutcomesClean27.6dVirgiRenamedInterventions.xlsx", na = "NA")


```

```{r, include=FALSE}
# prepare the data
DATApairs=pairwise(treat=Drug_name, mean=PolySomnographyScaleMean, sd=PolySomnographyScaleSD, n=PolySomnographyScaleParticipants, data=DATA, studlab = Study_name, sm= "MD")


# check there is no NA is the data
DPs <- DATApairs[!is.na(DATApairs$TE) & !is.na(DATApairs$seTE),]

#check p-value availability for paired t-test for crossover studies with both phases used
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,c("Study_name","treat1","treat2")]

# no p-value available for this outcome so remove crossover study
DPs <- DPs[DPs$studlab!="Garfinkel 1995",]

# save adjusted pairwise dataset for MAs
write.csv(DPs, file = "~/Virginia/NMA insomnia/PolysonographyTotSleepTime_pairwise.csv")


# run netconnection first to check for potential sub-networks
netconnection(treat1,treat2,studlab,data=DPs,warn = T)

#remove rows for studies disconnected from main network
DPs <- DPs[-grep("LAT|MAT|BBT I",DPs$treat1),]
# remove studies with "special patients" that should not be included in main analysis
# DPs <- DPs[DPs$Included==1,]



polyTST<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="MD",r="pbo",comb.fixed =F, comb.random = T)
polyTST

```

## Description of the network


Below is a description for the network formed by studies examining the outcome Total sleep time by polysomnography.

Number of included interventions:
```{r, echo=FALSE}
polyTST$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
polyTST$k
```

The following treatments were excluded as they were disconnected to the main network:

  * MAT
  * LAT
  * MAT+LAT
  * BBT I
  * self-monitoring control
  
The crossover study Garfinkel 1995 was also excluded because no p-value was available for this outcome.
  
\    

  
 The plot below shows the available data\
```{r, echo=FALSE}
#network plot
netgraph(polyTST, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```




## Frequentist network meta-analysis 

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(polyTST, ref="pbo", sortvar = Pscore,xlab="MD")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leaguePolyTST <- netleague(polyTST, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leaguePolyTST$random, file = "leaguePolyTST-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(polyTST$tau,3)))
```
and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(polyTST$I2, digits = 2)*100,"%"))
```

<!-- There is little/no/important evidence of inconsistency in the data. There are in total -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- split=netsplit(SOL) -->
<!-- SIDEp=split$compare.random$p -->
<!-- SIDEp=SIDEp[!is.na(SIDEp)] -->
<!-- #proportion of inconsistent loops -->
<!-- cat(length(SIDEp)) -->
<!-- ``` -->

<!-- comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in -->

<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(length(SIDEp[SIDEp<=0.1])) -->
<!-- ``` -->
<!-- loops which gives a % of inconsistent loops equal to -->
<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%")) -->
<!-- ``` -->



<!-- The p-value from the design-by-treatment test is -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- a=decomp.design(SOL) -->
<!-- print(round(a$Q.inc.random$pval,3)) -->
<!-- ``` -->

