---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 23rd July, refers to a single outcome analysis (Total Sleep Time) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->


```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoIncludedAllOutcomesClean27.6dVirgiRenamedInterventions.xlsx", na = "NA")


```



```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=Drug_name,mean=SleepTimeTotalScaleMean,sd=SleepTimeTotalScaleSD,n=SleepTimeTotalScaleParticipants, data=DATA, studlab = Final_ID_all, sm= "SMD")
#run NMA and create an object called EFF for efficacy   ### gives error because consists of 5 separate sub-networks so run netconnection first
netconnection(treat1,treat2,studlab,data=DATApairs,warn = T)
#remove rows for studies disconnected from main network
DPs <- DATApairs[-grep("LAT|MAT|BBT I|midazolam|hygiene|juice",DATApairs$treat1),]
#check p-value availability for paired t-test for crossover studies with both phases used
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,c("studlab","tst_PorF-value","tst_p=0, f=1")]
# use threshold value for those with p-value <0.001
DPs[DPs$studlab==185, "tst_PorF-value"] <- 0.00099
#now calculate adjusted SE for remaining crossover studies
DPs$tvalue <- qt(as.numeric(DPs$`tst_PorF-value`)/2, df=DPs$n1-1, lower.tail = F)
DPs$SDd <- abs((DPs$mean2-DPs$mean1)/DPs$tvalue*sqrt(DPs$n1))
DPs$rho <- (DPs$sd1^2 + DPs$sd2^2 - DPs$SDd^2)/(2*DPs$sd1*DPs$sd2)
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,"seTE"] <- sqrt((1/DPs$n1+(DPs$TE^2)/(2*DPs$n1))*(2-2*DPs$rho))[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1] 


#   EFF<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="SMD",r="pbo",comb.fixed =F, comb.random = T, tol.multiarm = 0.05, details.chkmultiarm = T)    
    ### gives error: Problems in multi-arm studies! Studies with negative treatment   arm variance: '18', '185'

# assign other correlation value to study 18 and 185 based on other studies
DPs[,c("studlab","rho")]
DPs[DPs$studlab==18|DPs$studlab==185,"rho"] <- 0.9
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,"seTE"] <- sqrt((1/DPs$n1+(DPs$TE^2)/(2*DPs$n1))*(2-2*DPs$rho))[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1] 
TST<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="SMD",r="pbo",comb.fixed =F, comb.random = T, tol.multiarm = 0.05)
TST

```
## Description of the network


Below is a description for the network formed by studies examining the outcome Total Sleep Time.


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included interventions:
```{r, echo=FALSE}
TST$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
TST$k
```

The following treatments were excluded as they were disconnected to the two main sub-networks:

  * MAT
  * LAT
  * MAT+LAT
  * sleep hygiene
  * lormetazepam + sleep hygiene
  * BBT I
  * self-monitoring control
  * midazolam
  * oxazepam
  * artificial juice
  * tart cherry juice  
  
\    

  
 The plot below shows the available data\
```{r, echo=FALSE}
#network plot
netgraph(TST, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1)
```




## Frequentist network meta-analysis 

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(TST, ref="pbo", sortvar = -Pscore,xlab="SMD")
```


The P-scores (equivalent to the SUCRAs) are shown below
```{r, echo=FALSE}
netrank(TST, small.values = "bad")
```

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(TST$tau,3)))
```
and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(TST$I2),"%"))
```



<!-- There is little/no/important evidence of inconsistency in the data. There are in total -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- split=netsplit(TST) -->
<!-- SIDEp=split$compare.random$p -->
<!-- SIDEp=SIDEp[!is.na(SIDEp)] -->
<!-- #proportion of inconsistent loops -->
<!-- cat(length(SIDEp)) -->
<!-- ``` -->

<!-- comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in -->

<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(length(SIDEp[SIDEp<=0.1])) -->
<!-- ``` -->
<!-- loops which gives a % of inconsistent loops equal to -->
<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%")) -->
<!-- ``` -->



<!-- The p-value from the design-by-treatment test is -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- a=decomp.design(TST) -->
<!-- print(round(a$Q.inc.random$pval,3)) -->
<!-- ``` -->


### Sensitivity analyses and meta-regressions

We run a sensitivity analyses excluding the crossover studies
```{r, include=FALSE}

#only non-crossover
InsoTSTsen=subset(DPs,Crossoverstudy!=1 &`crossover, not first phase used`!=1)  ### can I just take a subset of the previous pairwise dataset? or do I need to do a subset of the original dataset and then do the pairwise again?
TSTsens<-netmeta(TE,seTE,treat1,treat2,studlab,data=InsoTSTsen,  sm="SMD",comb.fixed =F, comb.random = T)
TSTsens


```

```{r, echo=FALSE}

forest(TSTsens, ref="pbo",sortvar = -Pscore, smlab="Only parallel studies", fontsize=10)


```


