---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 28th July, refers to a single outcome analysis (Sleep Quality) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->


```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
library(xlsx)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoIncludedAllOutcomesClean27.6dVirgiRenamedInterventions.xlsx", na = "NA")

```




```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=Drug_name,mean=SleepQualityScaleMean,sd=SleepQualityScaleSD,n=SleepQualityScaleParticipants, data=DATA, studlab = Final_ID_all, sm= "SMD")
#run NMA and create an object called EFF for efficacy   ### gives error because consists of 5 separate sub-networks so run netconnection first
netconnection(treat1,treat2,studlab,data=DATApairs,warn = T)
#remove rows for studies disconnected from main network
DPs <- subset(DATApairs, treat1!="BBT I" & treat1!="auricular acupuncture")
DPs <- DPs[-grep("LAT|MAT|acupressure|waitlist|therapeutic|hygiene|juice",DPs$treat2),]
#check p-value availability for paired t-test for crossover studies with both phases used
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,c("studlab","squal_PorF-value","squal_p=0, f=1")]
# use threshold value for those with p-value <0.025
DPs[DPs$studlab==17, "squal_PorF-value"] <- 0.02499
# remove studies for which no p-value available
DPs <- DPs[DPs$studlab!=94 & DPs$studlab!=21,]
# now calculate adjusted SE for remaining crossover studies
DPs$tvalue <- qt(as.numeric(DPs$`squal_PorF-value`)/2, df=DPs$n1-1, lower.tail = F)
DPs$SDd <- abs((DPs$mean2-DPs$mean1)/DPs$tvalue*sqrt(DPs$n1))
DPs$rho <- (DPs$sd1^2 + DPs$sd2^2 - DPs$SDd^2)/(2*DPs$sd1*DPs$sd2)
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,"seTE"] <- sqrt((1/DPs$n1+(DPs$TE^2)/(2*DPs$n1))*(2-2*DPs$rho))[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1] 


#   EFF<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="SMD",r="pbo",comb.fixed =F, comb.random = T, tol.multiarm = 0.05, details.chkmultiarm = T)    
    ### gives error: Problems in multi-arm studies! Studies with negative treatment   arm variance: '18', '185'

# assign other correlation value to study 18 and 185 based on other studies
# DPs[,c("studlab","rho")]
# DPs[DPs$studlab==18|DPs$studlab==185,"rho"] <- 0.9
# DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,"seTE"] <- sqrt((1/DPs$n1+DPs$TE/(2*DPs$n1))*(2-2*DPs$rho))[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1] 
# SQ<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs, sm="SMD",r="nitrazepam",comb.fixed =F, comb.random = T)
# SQ    ### after removing comparison with missing data network has 2 subnetworks


DPs1 <- DPs[-grep("chlormethiazole|triazolam|loprazolam|nitrazepam|zopiclone",DPs$treat2),]
# SQ1<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs1, sm="SMD",r="pbo",comb.fixed =F, comb.random = T, details.chkmultiarm=TRUE)
DPs1[,c("studlab","rho")]
DPs1[DPs1$studlab==18,"rho"] <- 0.9
DPs1[DPs1$Crossoverstudy==1 & DPs1$`crossover, not first phase used`==1,"seTE"] <- sqrt((1/DPs1$n1+(DPs1$TE^2)/(2*DPs1$n1))*(2-2*DPs1$rho))[DPs1$Crossoverstudy==1 & DPs1$`crossover, not first phase used`==1] 
SQ1<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs1, sm="SMD",r="pbo",comb.fixed =F, comb.random = T)
SQ1

```

## Description of the network

This network formed by studies examining the outcome Sleep Quality is composed by two sub-networks.
The following treatments were excluded as they were disconnected to the two main sub-networks:

* MAT
* LAT
* MAT+LAT
* therapeutic touch
* control/no intervention
* mimic therapeutic touch
* Mindfulness Based Stress Reduction Program
* waitlist
* sleep hygiene
* lormetazepam + sleep hygiene
* BBT I
* self-monitoring control
* auricular acupuncture
* control?
* acupressure
* sham acupressure
* artificial juice
* tart cherry juice 


### Sub-network 1

Below is a description for the sub-network including the following interventions

```{r, echo=FALSE}
SQ1$trts
```


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included interventions:
```{r, echo=FALSE}
SQ1$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
SQ1$k
```



The plot below shows the available data

```{r, echo=FALSE}

#network plot
netgraph(SQ1, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```


Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(SQ1, ref="pbo", sortvar = Pscore,xlab="SMD")
```
```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leagueSQ1 <- netleague(SQ1, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leagueSQ1$random, file = "leagueSQ1-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```

<!-- The P-scores (equivalent to the SUCRAs) are shown below -->
<!-- ```{r, echo=FALSE} -->
<!-- netrank(SQ1) -->
<!-- ``` -->

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(SQ1$tau,3)))
```
and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(SQ1$I2, digits = 2)*100,"%"))
```

<!-- There is little/no/important evidence of inconsistency in the data. There are in total -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- split=netsplit(SQ1) -->
<!-- SIDEp=split$compare.random$p -->
<!-- SIDEp=SIDEp[!is.na(SIDEp)] -->
<!-- #proportion of inconsistent loops -->
<!-- cat(length(SIDEp)) -->
<!-- ``` -->

<!-- comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in -->

<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(length(SIDEp[SIDEp<=0.1])) -->
<!-- ``` -->
<!-- loops which gives a % of inconsistent loops equal to -->
<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%")) -->
<!-- ``` -->



<!-- The p-value from the design-by-treatment test is -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- a=decomp.design(SQ1) -->
<!-- print(round(a$Q.inc.random$pval,3)) -->
<!-- ``` -->




```{r, include=FALSE}
SQ2 <- netmeta(TE,seTE,treat1,treat2,studlab,data=DPs, subset = grep("chlormethiazole|triazolam|loprazolam|nitrazepam",DPs$treat1), sm="SMD",r="chlormethiazole",comb.fixed =F, comb.random = T)
SQ2
```

### Sub-network 2

Below is a description for the sub-network including the following interventions

```{r, echo=FALSE}
SQ2$trts
```


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included interventions:
```{r, echo=FALSE}
SQ2$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
SQ2$k
```



The plot below shows the available data

```{r, echo=FALSE}

#network plot
netgraph(SQ2, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1)
```

Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(SQ2, ref="chlormethiazole", sortvar = Pscore,xlab="SMD")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# create league table and export as excel
leagueSQ2 <- netleague(SQ2, digits = 2, bracket = "(", separator = " to ")
write.xlsx(leagueSQ2$random, file = "leagueSQ2-random.xls",
         sheetName = "leaguetable (random)", col.names = F, row.names = F)
```

<!-- The P-scores (equivalent to the SUCRAs) are shown below -->
<!-- ```{r, echo=FALSE} -->
<!-- netrank(SQ2) -->
<!-- ``` -->

<!-- The heterogeneity standard deviation is estimated at -->
<!-- ```{r, echo=FALSE} -->
<!-- cat(paste("tau=",round(SQ2$tau,3))) -->
<!-- ``` -->
<!-- and I-square (total) is  -->
<!-- ```{r, echo=FALSE} -->
<!-- cat(paste("I2=",round(SQ1$I2),"%")) -->
<!-- ``` -->


### Sensitivity analyses and meta-regressions

We run a sensitivity analyses on the first sub-network excluding the crossover studies.
```{r, include=FALSE}

#only non-crossover
InsoSQsen=subset(DPs1,Crossoverstudy!=1 &`crossover, not first phase used`!=1)  ### can I just take a subset of the previous pairwise dataset? or do I need to do a subset of the original dataset and then do the pairwise again?
SQ1sens<-netmeta(TE,seTE,treat1,treat2,studlab,data=InsoSQsen,  sm="SMD",comb.fixed =F, comb.random = T)
SQ1sens


```

```{r, echo=FALSE}

#network plot
netgraph(SQ1sens, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```

```{r, echo=FALSE}

forest(SQ1sens, ref="pbo",sortvar = Pscore, smlab="Only parallel studies", fontsize=10)


```
