---
title: "Insomnia NMA"
subtitle: "Prepared by Virginia Chiocchia on 9th October, refers to sensitivity analyses for a single outcome (Sleep Quality) in a frequentist setting"
output: 
  word_document: 
    fig_height: 7
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Make sure you have the needed libraries from R-Cran and Github: -->
<!-- devtools -->
<!-- NMAJags -->
<!-- R2jags -->
<!-- netmeta -->
<!-- meta -->
<!-- metafor -->
<!-- readxl -->


```{r, include=FALSE}
library(devtools)
install_github("esm-ispm-unibe-ch/NMAJags")
library(NMAJags)
library(R2jags)
library(netmeta)
library(meta)
library(metafor)
library(readxl)
library(xlsx)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
### no need for sensitivity analysis including psychogeriatric patients as only study including them for this outcome is disconnected to the rest of the network  

#get the data and select them
DATA <- read_excel("~/Virginia/NMA insomnia/Insomnia/MyrtoClean4.10VirgiRenamedIntervSideEffectsClean.xlsx", na = "NA")

```




```{r, include=FALSE}
#prepare the data
DATApairs=pairwise(treat=`Drug Group`,mean=SleepQualityScaleMean,sd=SleepQualityScaleSD,n=SleepQualityScaleParticipants, data=DATA, studlab = Final_ID_all, sm= "SMD")
#run NMA and create an object called EFF for efficacy   ### gives error because consists of 5 separate sub-networks so run netconnection first
netconnection(treat1,treat2,studlab,data=DATApairs,warn = T)

#remove rows for studies disconnected from main network
DPs <- subset(DATApairs, treat1!="BBT I" & treat1!="auricular acupuncture")
DPs <- DPs[-grep("LAT|MAT|acupressure|waitlist|therapeutic|hygiene|juice",DPs$treat2),]
#check p-value availability for paired t-test for crossover studies with both phases used
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,c("studlab","squal_PorF-value","squal_p=0, f=1")]
# use threshold value for those with p-value <0.025
DPs[DPs$studlab==17, "squal_PorF-value"] <- 0.02499
# remove studies for which no p-value available
DPs <- DPs[DPs$studlab!=21,]
# now calculate adjusted SE for remaining crossover studies
DPs$tvalue <- qt(as.numeric(DPs$`squal_PorF-value`)/2, df=DPs$n1-1, lower.tail = F)
DPs$SDd <- abs((DPs$mean2-DPs$mean1)/DPs$tvalue*sqrt(DPs$n1))
DPs$rho <- (DPs$sd1^2 + DPs$sd2^2 - DPs$SDd^2)/(2*DPs$sd1*DPs$sd2)
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,"seTE"] <- sqrt((1/DPs$n1+(DPs$TE^2)/(2*DPs$n1))*(2-2*DPs$rho))[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1] 


#   EFF<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs,  sm="SMD",r="pbo",comb.fixed =F, comb.random = T, tol.multiarm = 0.05, details.chkmultiarm = T)    
    ### gives error: Problems in multi-arm studies! Studies with negative treatment   arm variance: '18', '185'

# assign other correlation value to study 18 based on other studies


DPs[,c("studlab","rho")]
DPs[DPs$studlab==18,"rho"] <- 0.9
DPs[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1,"seTE"] <- sqrt((1/DPs$n1+(DPs$TE^2)/(2*DPs$n1))*(2-2*DPs$rho))[DPs$Crossoverstudy==1 & DPs$`crossover, not first phase used`==1] 

## one study with missing data but netmeta will exclude automatically
SQs<-netmeta(TE,seTE,treat1,treat2,studlab,data=DPs, sm="SMD",r="pbo",comb.fixed =F, comb.random = T)
SQs

```

## Description of the network - sensitivity analysis (by drug group)

The following treatments were excluded as they were disconnected to the two main network:

* MAT
* LAT
* MAT+LAT
* therapeutic touch
* control/no intervention
* mimic therapeutic touch
* Mindfulness Based Stress Reduction Program
* waitlist
* sleep hygiene
* lormetazepam + sleep hygiene
* BBT I
* self-monitoring control
* auricular acupuncture
* control?
* acupressure
* sham acupressure
* artificial juice
* tart cherry juice 



Below is a description for the network formed by studies examining the outcome Sleep Quality analysed by drug groups.

```{r, echo=FALSE}
SQs$trts
```


<!-- Below are the total number of participants in each of the included interventions -->
<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- #describe the data -->
<!-- tapply(DATAs$N_arm_total_stapf,DATAs$Drug_name,sum,na.rm=T) -->

<!-- ``` -->
Number of included interventions:
```{r, echo=FALSE}
SQs$n
```
Number of included studies:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
SQs$k
```



The plot below shows the available data

```{r, echo=FALSE}

#network plot
netgraph(SQs, plastic=F, thickness="number.of.studies", multiarm = F, points=T, col=1, number.of.studies=T)
```


Below are the relative treatment effects from the NMA model. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#forest plots
forest(SQs, ref="pbo", sortvar = Pscore,xlab="SMD")
```

<!-- The P-scores (equivalent to the SUCRAs) are shown below -->
<!-- ```{r, echo=FALSE} -->
<!-- netrank(SQ1) -->
<!-- ``` -->

The heterogeneity standard deviation is estimated at
```{r, echo=FALSE}
cat(paste("tau=",round(SQs$tau,3)))
```
and I-square (total) is 
```{r, echo=FALSE}
cat(paste("I2=",round(SQs$I2, digits = 2)*100,"%"))
```

<!-- There is little/no/important evidence of inconsistency in the data. There are in total -->

<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- split=netsplit(SQ1) -->
<!-- SIDEp=split$compare.random$p -->
<!-- SIDEp=SIDEp[!is.na(SIDEp)] -->
<!-- #proportion of inconsistent loops -->
<!-- cat(length(SIDEp)) -->
<!-- ``` -->

<!-- comparisons in the network, and there is inconsistency (according to SIDE p-value<0.10) in -->

<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(length(SIDEp[SIDEp<=0.1])) -->
<!-- ``` -->
<!-- loops which gives a % of inconsistent loops equal to -->
<!-- ```{r, echo=F, message=FALSE, warning=FALSE} -->
<!-- cat(paste(round((length(SIDEp[SIDEp<=0.1])/length(SIDEp))*100,1),"%")) -->
<!-- ``` -->



<!-- The p-value from the design-by-treatment test is -->

<!-- ```{r, echo=FALSE, message=FALSE, warning=FALSE} -->
<!-- a=decomp.design(SQ1) -->
<!-- print(round(a$Q.inc.random$pval,3)) -->
<!-- ``` -->
